Dual terminal sliding mode control

### 2016-05-15 paper3_manuscript.tex
20160515

&\Vert M(\bm q)\Vert< \theta_0\\
&\Vert C(\bm q,\dot {\bm q})\Vert< \phi_0+\phi_1\Vert\bm q\Vert+\phi_2\Vert\dot{\bm q}\Vert^2\\
&\Vert g(\bm q)\Vert< \psi_0+\psi_1\Vert\bm q\Vert\\
&\Vert \bm {\rho}(t)\Vert< \mu_0+\mu_1\Vert\bm q\Vert+\mu_2\Vert\dot{\bm q}\Vert^2,

@@

\begin{align}
\begin{bmatrix}
m_{12}(q_2) &m_{12}(q_2)\\
m_{21}(q_2) &m_{22}
\end{bmatrix}
\begin{pmatrix}
\ddot q_1\\
\ddot q_2
\end{pmatrix}
+
\begin{bmatrix}
-c(q_2)\dot q_1^2-2c(q_2)\dot q_1\dot q_2\\
c(q_2)\dot q_2^2
\end{bmatrix}+
\begin{bmatrix}
\xi_1(q_1,q_2) g\\
\xi_2(q_1,q_2) g
\end{bmatrix}=
\begin{pmatrix}
\tau_1\\
\tau_2
\end{pmatrix},
\end{align}
where
\begin{align*}
&m_{11}(q_2)=(m_1+m_2)r_1^2+m_2r_2^2+2m_2r_1r_2\cos(q_2)+J_1,\\
&m_{12}(q_2)=m_2r_2^2+m_2r_1r_2\cos(q_2),\\
&m_{21}(q_2)=m_{12}(q_2),\\
&m_{22}=m_2r_2^2+J_2,\\
&c(q_2)=m_2r_1r_2\sin(q_2),\\
&\xi_1(q_1,q_2) =(m_1+m_2)r_1\cos(q_2)+m_2r_2\cos(q_1+q_2),\\
&\xi_2(q_1,q_2) = m_2r_2\cos(q_1+q_2).
\end{align*}\par
The values of the parameters are listed here, $r_1=1m$, $r_2=0.8m$, $J_1=5 kgm$, $J_2=5kgm$, $m_1=0.5kg$, $m_2=1.5kg$.
\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{paper3_fig4.eps}
\caption{2}
\label{Figure:4}
\end{figure}

>>>>

&\Vert M(\bm q)\Vert< \theta_0\notag\\
&\Vert C(\bm q,\dot {\bm q})\Vert< \phi_0+\phi_1\Vert\bm q\Vert+\phi_2\Vert\dot{\bm q}\Vert^2\notag\\
&\Vert g(\bm q)\Vert< \psi_0+\psi_1\Vert\bm q\notag\Vert
&\Vert \bm {\rho}(t)\Vert< \mu_0+\mu_1\Vert\bm q\Vert+\mu_2\Vert\dot{\bm q}\Vert^2,\label{eq:manipulator uncertainty}

@@

\begin{align}
\begin{bmatrix}
m_{12}(q_2) &m_{12}(q_2)\\
m_{21}(q_2) &m_{22}
\end{bmatrix}
\begin{pmatrix}
\ddot q_1\\
\ddot q_2
\end{pmatrix}
+
\begin{bmatrix}
-c(q_2)\dot q_1^2-2c(q_2)\dot q_1\dot q_2\\
c(q_2)\dot q_2^2
\end{bmatrix}+
\begin{bmatrix}
\xi_1(q_1,q_2) g\\
\xi_2(q_1,q_2) g
\end{bmatrix}=
\begin{pmatrix}
\tau_1\\
\tau_2
\end{pmatrix},
\end{align}
where
\begin{align*}
&m_{11}(q_2)=(m_1+m_2)r_1^2+m_2r_2^2+2m_2r_1r_2\cos(q_2)+J_1,\\
&m_{12}(q_2)=m_2r_2^2+m_2r_1r_2\cos(q_2),\\
&m_{21}(q_2)=m_{12}(q_2),\\
&m_{22}=m_2r_2^2+J_2,\\
&c(q_2)=m_2r_1r_2\sin(q_2),\\
&\xi_1(q_1,q_2) =(m_1+m_2)r_1\cos(q_2)+m_2r_2\cos(q_1+q_2),\\
&\xi_2(q_1,q_2) = m_2r_2\cos(q_1+q_2).
\end{align*}\par
The values of the parameters are listed here, $r_1=1m$, $r_2=0.8m$, $J_1=5 kgm$, $J_2=5kgm$, $m_1=0.5kg$, $m_2=1.5kg$. In this model, the uncertainty is brought in by estimated terms, namely, $\bar m_1=0.4$ and $\bar m_2=1.2$ which are all not the actuate value obviously. In addition, owing to that it sits on many terms in the dynamic equations, it's a severe challenge to guarantee the performance. Accordingly, the uncertainty parameters in Eq.~(\ref{eq:manipulator uncertainty}) are assumed to be $\mu_0=10$, $\mu_1=3$, $\mu_2=3$.\par
This section will give a set of simulation to examine the performance of the MDSM control in tracking the certain angle condition. The behavior of the manipulator should fulfill the initial and desired condition, namely, $(\bm q_0^T, \dot{\bm q}_0^T)= (0.3,0.2,0,0)$ and $({\bm q}_d^T,\dot{\bm q}_d^T)=(1,1,0,0)$. In order to ensure the stability and a fast convergent speed, the control parameters are chosen conservatively to make the manipulator track the desired attitude in finite time, and these parameters are $\alpha = 0.6$, $\gamma = 1$, $\lambda = 0.1$, $\eta = 100$. The terminal sliding mode control (TSM) scheme, as a comparison, is also implemented to regulate the behavior of the manipulator, the main control parameters of which are selected as $\alpha = 0.6$, $\gamma = 5$ and $\eta = 150$ to get a fairly good control performance.\par
The performance of the controllers mentioned above is illustrated in Figure~\ref{Figure:4} and Figure~\ref{Figure:5}.
\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{paper3_fig4.eps}
\caption{2}
\label{Figure:4}
\end{figure}
